{\vspace{-2cm}}Temporal Congestion Analysis and Predictive Modeling of Ride-Hailing Trips in NYC Using High-Volume FHV Data

### 2025-04-22 paper.tex
chore: Draft paper.

\section{Abstract}
This study outlines a potential project to explore traffic congestion patterns in New York City by analyzing High-Volume For-Hire Vehicle (FHV) trip records from services like Uber and Lyft. Using publicly available data from all twelve months of 2024, the proposed analysis would examine how trip durations and speeds vary by time of day, day of week, and provider. After preprocessing in Apache Spark (PySpark), I plan to identify temporal trends and build predictive models in R using linear and logistic regression. The project is designed to demonstrate how the size and complexity of the dataset require the use of big data tools for processing and modeling.

>>>>

\section{Abstract}
This study outlines a potential project to explore traffic congestion patterns in New York City by analyzing High-Volume For-Hire Vehicle (FHV) trip records from ride-sharing services such as Uber and Lyft. Using publicly available data from all twelve months of 2024, the proposed analysis would examine how trip durations and speeds vary by time of day, day of week, and provider. After preprocessing in Apache Spark (PySpark), I plan to identify temporal trends and build predictive models in R using linear and logistic regression. The project is designed to demonstrate how the size and complexity of the dataset require the use of big data tools for processing and modeling.
